\normalfont \normalsize \textsc{Exoplanet Patchy Cloud Project} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Data Preparation\\ \horrule{2pt} \\[0.5cm]

### 2014-11-03 summary/AperturePhot1/aperPhotSummary.tex
start writing summary doc on aperture photometry

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Data Preparation\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\maketitle % Print the title
\section{Summary}
\begin{enumerate}
\item Cross correlation has the best performance for locating the
  centroids of star images.
\item Bicubic interpolation generates smaller RMS fluctuation
  comparing to \texttt{FSHIFT.pro} when shift images, but does not
  strictly obey flux conservation. \texttt{FSHIFT.pro} strictly keeps
  the conservation of flux. Bicubic interpolation causes artifacts
  around the star images.
\end{enumerate}

\section{Centroid of Primary Star}
4 methods to locate the centroid of the primary objects were tested
for all 78 cosmic ray removed images of ABPIC-B. I compared the 4 sets
of results in order to determine the best method to find star image
centroid in this situation where the image is slightly saturated.\par

\subsection{Method Introduction}

\begin{enumerate}
\item \texttt{CNTRD.PRO}\\
  IDL routine \texttt{CNTRO.PRO} locates the position where the X
  and Y derivatives go to zero. The search area of \texttt{CNTRO.PRO}
  can be adjusted with parameter \texttt{EXTENDBOX}.\par
\item \texttt{GCNTRD.PRO}\\
  IDL routine \texttt{GCNTRD.PRO} fits the star image with a 2D-Gaussian
  function to search for centroid. The search area cannot be defined
  in this routine. \texttt{GCNTRD.pro} is likely to fail when the
  initial guess of centroid coordinates are far away from the true
  values. This is inconvenient for pipeline scenario, where images
  of different dithering positions are assigned with same initial
  values for fitting. In practice, I ran \texttt{CNTRD.PRO} before
  \texttt{GCNTRD.PRO} to provide initial values for Gaussian fitting.\par
\item Cross Correlation\\
  Calculate the cross correlation value to align images. The images
  taken with different rolling angle were treat separately. Images
  taken in 1st, 3th, and 5th orbits were calculated cross correlation
  with the first image in 1st orbit and images taken in 2nd, 4th, and
  6th orbits with first image in 2nd orbit.\par
 \item World Coordinate System(WCS)\\
   Use WCS to align every image. The treatment with different rolling
   angles is the same as cross correlation method. Centroids were
   calculated with IDL routine \texttt{XYXY.pro}.\par
\end{enumerate}

\subsection{Result Comparison}
Figure \ref{fig:x_off} and \ref{fig:y_off} demonstrates the
distributions of centroid offsets of \texttt{GCNTRD.pro}, cross
correlation, and WCS relative to the \texttt{CNTRD.pro} method in $x$
and $y$ direction. \par

According to the two plots, most of results calculated with all four
methods are constrained within $\pm 0.2$ pixels. Both in $x$ and $y$
directions, the histograms of \texttt{GCNTRD.pro} offsets have a
fairly strange shape, while the distributions of cross correlation and
WCS methods' offsets show a Gaussian like shape. In $x$-direction, the
distributions of cross correlation and WCS have similar behavior that
the centers of two histograms both have $\sim -0.1$ pixels offset. In
$y$ direction, histogram of cross correlation demonstrates that the
results for cross correlation and \texttt{CNTRD.pro} are well
agreed. The histogram of WCS is skewed and has a $\sim -0.1$ pixels
offset.\par

To sum, \texttt{GCNTRD.pro} method has the worst performance. In
$x$-direction, the results for cross correlation and WCS agrees well
and in $y$-direction the results for cross correlation and
\texttt{CNTRD.pro} agrees well. Thus cross correlation method performs
best.\par

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{x_off}
  \caption{$x$-direction offset histogram}
  \label{fig:x_off}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{y_off}
  \caption{$y$-direction offset histogram}
  \label{fig:y_off}
\end{figure}

\section{Image shift and interpolation algorithm}

I tested two image shift methods that uses two different interpolation
algorithms. The two algorithms are bicubic interpolation and bilinear
interpolation(used by  IDL routine \texttt{FSHIFT.pro}).\par

To evalueate the two shift methods, the image is shifted in a random direction
with a specific length and then shifted back. Both the root mean
square and mean flux change between the original image and the
modified image  will be calculated as following:
\begin{align}
  &\Delta_{\mathrm{rms}} = \frac{\sqrt{(\mathrm{img}_{0} -
      \mathrm{img_{shifted}})^{2}}}{N_{\mathrm{pixels}}}\\
  &\bar{\Delta} = \frac{\mathrm{img}_{0} - \mathrm{img_{shifted}}}{N_{\mathrm{pixels}}}
\end{align}

The results are demonstrated with figure \ref{fig:shifted}.
\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{test_shift}
  \caption{Root mean square and mean flux change betwenn the original image and the modified image as a function of shift length.}
  \label{fig:shifted}
\end{figure}
\begin{enumerate}
\item bicubic interpolation comes up with a smaller RMS change, thus
  the error generated by image shift will be smaller with a bicubic interpolation.
\item \texttt{FSHIFT.pro} strictly keeps flux conserved, while bicubic
  interpolation ends up with a $\sim \pm 0.003$ per pixel change in flux.
\item bicubic interpolation will generate ringing artifacts(figure \ref{fig:ringing})
\end{enumerate}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\textwidth]{interpolated}
  \caption{Ringing artifacts generated by bicubic interpolation.}
  \label{fig:ringing}
\end{figure}
\end{document}

>>>>

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Cross Correlation Test and Preliminary Aperture Photometry Result\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\maketitle % Print the title
\section{Summary}
\begin{enumerate}
\item Cross Correlation method can align images with the saturated
  primary star centroid as precise as $\sim 0.01$ pixels, which is far
  better than the precision of IDL \texttt{cntrd.pro} or
  \texttt{gcntrd.pro} which is more than $\sim 0.2$ pixels. According
  to the residual image patterns, cross correlation alignment has
  better performance tan WCS alignment.
\item Aperture photometry for secondary object in ABPIC system is
  measured. The light curves are very similar to Glenn's
  measurement. However, the light curves for two filters, F125W and
  F160W agree with each other better in my measurement.
\item Considering only statistical uncertainties (counting errors) and
  fluctuation in the background, a rough estimate gives a result of
  0.3\% for relative uncertainty for one
  photometry measurement.

\end{enumerate}
\section{Image Alignment}
\subsection{Alignment Precision Test}
\subsection{The Modification for IDL \texttt{crosscorr} Routine}
\subsection{PSF subtraction result}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{cc_example}
  \includegraphics[width=\textwidth]{wcs_example}
  \caption{PSF subtraction comparison}\label{fig:subcomp}
\end{figure}
\section{Aperture Photometry Result}
\subsection{Light Curves}

The light curve measurements for both absolute fluxes and relative
fluxes are shown in Figure \ref{fig:lightcurve}. Figure
\ref{fig:glenn} is Glenn's preliminary measurements. The lower plot in
figure \ref{fig:lightcurve} is very similar to figure
\ref{fig:glenn}. However, in figure \ref{fig:glenn}, the light curves
for F125W and F160W show considerable discrepancies in 5th and 6th
orbits. However in my measurement, the two curves agree better. Apart
from this, the most prominent features are shown in both light
curves, e.g. the light curves are lower in 2nd orbit and the
discrepancy at start of the 3rd orbit.

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{fluxcurve_aper_05}
  \includegraphics[width=0.8\textwidth]{relativefluxcurve_aper_05}
  \caption{Filter F125W and F160W light curves. Upper images shows the
    curve for absolute flux (count per second) changing with time. The
    mean values for both light curves are plotted with gray dashed
    lines. In the lower image, two light curves are normalized with
    the mean value of itself.}
  \label{fig:lightcurve}
\end{figure}

\begin{figure}
  \centering
    \centering
    \includegraphics[width=0.8\textwidth]{ABPIC_DELTA_PERCENT_INITIAL}
    \caption{Glenn's preliminary measurement}
    \label{fig:glenn}
  \end{figure}

\subsection{Error Estimation}
Considering statistical uncertainty and fluctuation of background sky,
the relative error for one aperture photometry measurement is below
0.3\% according to my estimation. The error estimation procedure is
explained as following.\par

Statistical uncertainty:
\begin{equation}
  \sigma_{\mathrm{stat}}^{2}=ft_{\mathrm{expo}}
\end{equation}
Background fluctuation:
\begin{equation}
  \sigma_{\mathrm{sky}}^{2}=N\sigma_{\mathrm{sky,0}}^{2}t_{expo}
\end{equation}
Total error are the combination of these two parts:
\begin{equation}
  \sigma^{2} = \sigma_{\mathrm{stat}}^{2}+\sigma_{\mathrm{sky}}^{2}=ft_{\mathrm{expo}}+N\sigma_{\mathrm{sky,0}}^{2}t_{expo}
\end{equation}
Relative uncertainty:
\begin{equation}
  \frac{\sigma}{\mathrm{Flux}} = \frac{\sqrt{ft_{\mathrm{expo}}+N\sigma_{\mathrm{sky,0}}^{2}t_{expo}}}{ft_{\mathrm{expo}}}
\end{equation}
The exposure time are 30s for F125W images and 15s for F160W
images. Here I adopt 15s for a upper limit estimation. The flux
intensity for the exoplanet is $\sim 8000$ counts per second. The
standard deviation for background is $\sim 1$ counts per
second. Plugin those numbers, I estimated a relative uncertainty for 0.3\%.
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2014-11-03 summary/DataPreparation/_region_.tex
start writing summary doc on aperture photometry

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\documentclass[paper=letter, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size
\synctex=1
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
%\usepackage[nolists, nomarkers]{endfloat}
\usepackage{hyperref}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[section]{placeins}
\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps

@@

\setlength\parindent{0pt} % Removes all indentation from paragraphs -
                          % comment this line for an assignment with
                          % lots of text
\setlength\parskip{12pt}

@@

\maketitle % Print the title
\section{Summary}
\begin{enumerate}
\item Cross correlation has the best performance for locating the
  centroids of star images.
\item Bicubic interpolation generates smaller RMS fluctuation
  comparing to \texttt{FSHIFT.pro} when shift images, but does not
  strictly obey flux conservation. \texttt{FSHIFT.pro} strictly keeps
  the conservation of flux. Bicubic interpolation causes artifacts
  around the star images.
\end{enumerate}

\section{Centroid of Primary Star}
4 methods to locate the centroid of the primary objects were tested
for all 78 cosmic ray removed images of ABPIC-B. I compared the 4 sets
of results in order to determine the best method to find star image
centroid in this situation where the image is slightly saturated.\par

@@

\begin{enumerate}
\item \texttt{CNTRD.PRO}\\
  IDL routine \texttt{CNTRO.PRO} locates the position where the X
  and Y derivatives go to zero. The search area of \texttt{CNTRO.PRO}
  can be adjusted with parameter \texttt{EXTENDBOX}.\par
\item \texttt{GCNTRD.PRO}\\
  IDL routine \texttt{GCNTRD.PRO} fits the star image with a 2D-Gaussian
  function to search for centroid. The search area cannot be defined
  in this routine. \texttt{GCNTRD.pro} is likely to fail when the
  initial guess of centroid coordinates are far away from the true
  values. This is inconvenient for pipeline scenario, where images
  of different dithering positions are assigned with same initial
  values for fitting. In practice, I ran \texttt{CNTRD.PRO} before
  \texttt{GCNTRD.PRO} to provide initial values for Gaussian fitting.\par
\item Cross Correlation\\
  Calculate the cross correlation value to align images. The images
  taken with different rolling angle were treat separately. Images
  taken in 1st, 3th, and 5th orbits were calculated cross correlation
  with the first image in 1st orbit and images taken in 2nd, 4th, and
  6th orbits with first image in 2nd orbit.\par
 \item World Coordinate System(WCS)\\
   Use WCS to align every image. The treatment with different rolling
   angles is the same as cross correlation method. Centroids were
   calculated with IDL routine \texttt{XYXY.pro}.\par
\end{enumerate}

\subsection{Result Comparison}
Figure \ref{fig:x_off} and \ref{fig:y_off} demonstrates the
distributions of centroid offsets of \texttt{GCNTRD.pro}, cross
correlation, and WCS relative to the \texttt{CNTRD.pro} method in $x$
and $y$ direction. \par

According to the two plots, most of results calculated with all four
methods are constrained within $\pm 0.2$ pixels. Both in $x$ and $y$
directions, the histograms of \texttt{GCNTRD.pro} offsets have a
fairly strange shape, while the distributions of cross correlation and
WCS methods' offsets show a Gaussian like shape. In $x$-direction, the
distributions of cross correlation and WCS have similar behavior that
the centers of two histograms both have $\sim -0.1$ pixels offset. In
$y$ direction, histogram of cross correlation demonstrates that the
results for cross correlation and \texttt{CNTRD.pro} are well
agreed. The histogram of WCS is skewed and has a $\sim -0.1$ pixels
offset.\par

To sum, \texttt{GCNTRD.pro} method has the worst performance. In
$x$-direction, the results for cross correlation and WCS agrees well
and in $y$-direction the results for cross correlation and
\texttt{CNTRD.pro} agrees well. Thus cross correlation method performs
best.\par

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{x_off}
  \caption{$x$-direction offset histogram}
  \label{fig:x_off}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{y_off}
  \caption{$y$-direction offset histogram}
  \label{fig:y_off}
\end{figure}

\section{Image shift and interpolation algorithm}

I tested two image shift methods that uses two different interpolation
algorithms. The two algorithms are bicubic interpolation and bilinear
interpolation(used by  IDL routine \texttt{FSHIFT.pro}).\par

To evalueate the two shift methods, the image is shifted in a random direction
with a specific length and then shifted back. Both the root mean
square and mean flux change between the original image and the
modified image  will be calculated as following:
\begin{align}
  &\Delta_{\mathrm{rms}} = \frac{\sqrt{(\mathrm{img}_{0} -
      \mathrm{img_{shifted}})^{2}}}{N_{\mathrm{pixels}}}\\
  &\bar{\Delta} = \frac{\mathrm{img}_{0} - \mathrm{img_{shifted}}}{N_{\mathrm{pixels}}}
\end{align}

The results are demonstrated with figure \ref{fig:shifted}.
\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{test_shift}
  \caption{Root mean square and mean flux change betwenn the original image and the modified image as a function of shift length.}
  \label{fig:shifted}
\end{figure}
\begin{enumerate}
\item bicubic interpolation comes up with a smaller RMS change, thus
  the error generated by image shift will be smaller with a bicubic interpolation.
\item \texttt{FSHIFT.pro} strictly keeps flux conserved, while bicubic
  interpolation ends up with a $\sim \pm 0.003$ per pixel change in flux.
\item bicubic interpolation will generate ringing artifacts(figure \ref{fig:ringing})
\end{enumerate}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\textwidth]{interpolated}
  \caption{Ringing artifacts generated by bicubic interpolation.}
  \label{fig:ringing}
\end{figure}
\end{document}

>>>>

\message{ !name(summary.tex)}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage{bm}

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

@@

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

@@

\message{ !name(summary.tex) !offset(-3) }

\maketitle % Print the title
\section{Centroid of Primary Star}
4 methods were tested to locate the centroid of the primary objects
for all 78 cosmic ray removed images of ABPIC-B. I compared the
4 sets of results for each method in order to determine the best
method in this situation where the image of the primary star is
slightly saturated.\par

@@

\begin{enumerate}
\item \texttt{\textbf{CNTRD.PRO}}
\end{enumerate}

\end{document}
\message{ !name(summary.tex) !offset(-89) }
